---
title: '#Task1:TITANIC SURVIVAL PREDICTION'
author: "Aishani Dey"
date: "2023-08-09"
output:
  word_document: default
  html_document: default
---
## Loading the data and Omitting the na values:

```{r}
d=read.csv("C:/Users/Aishani/Downloads/tested.csv")
k=is.na(d)
d1=na.omit(d)
```

## Calling the important libraries and obtaining the structure of the data:

```{r}
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(gridExtra)
glimpse(d)
```

## Visualizing Age, Passenger-Class and Sex wrt survival status where 1 denotes survived/alive and 0 denotes not survived/dead.

```{r}
g1=ggplot(d1,aes(Age,fill=as.factor(Survived)))+geom_density(aes(y=..density..),col=1,alpha=0.5)+
 scale_fill_brewer(palette="Set1")+labs(fill="Survial Status");g1
```

### Observation:

a)Most of the passengers died at the age between 20 to 40 and the survival rate is also high at this age.

b)After 60, the rate of survival decreases.

```{r}
g2=ggplot(d1,aes(Pclass,fill=as.factor(Survived)))+geom_bar(position="dodge")+scale_fill_brewer(palette="Set1")+labs(fill="Survial Status");g2
```

### Observation:

a)The survival rate of the 1st class passengers are almost equal to their fatal rate.

b)The survival rate for 2nd class and 3rd class passengers decreases.

```{r}
g3=ggplot(d1,aes(Sex,fill=as.factor(Survived)))+geom_bar(position="dodge")+scale_fill_brewer(palette="Set2")+labs(fill="Survial Status");g3
```

### Observation:

a)From the graph we can see,The females are only survived and males are died more than the number of females survived.

```{r}
table(sex=d1$Sex,status=d1$Survived)
```



## training the model and testing the validity:

Here, we fit a logistic regression model on the training data since we have our response (survival status) as binary variable.
 we have taken our covariates as Age,Pclass,Fare,Embarked.

```{r}
set.seed(seed=1)
s=sample(c("T","F"),nrow(d1),prob=c(0.7,0.3),replace=T)
train=subset(d1,s=="T")
test=subset(d1,s=="F")
train$Pclass=as.factor(train$Pclass)
test$Pclass=as.factor(test$Pclass)
model=glm(Survived~Age+Pclass+Fare+Embarked,train,family=binomial(link="logit"))
pred=as.numeric(predict(model,type="response",newdata=test))
```

###### After fitting the model, we construct confusion matrix using th test data taking the cut off value as 0.5.

```{r}
library(ModelMetrics)
m=confusionMatrix(test$Survived,pred,cutoff = 0.5);m
```

### We now find the Misclassification Rate as follows:

```{r}
misclassification_error=(26+5)/95;misclassification_error
```

##### It comes out as almost 33%.

### We test the accuracy of the model through ROC curve.

```{r}
library(pROC)
roc(test$Survived~pred,plot=T,print.auc=TRUE)
```

### Since the area under the curve is almost 0.64 that is our model has 64% accuracy.